---
title: "PPE_Core_Microbiota"
author: "Camilo G치lvez A."
output: html_document
---

#libraries
```{r libraries, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(data.table)
library(Biostrings)
library(DECIPHER)
library(vegan)
library(UpSetR)
library(leaflet)
library(dendextend)
library(treemap)
library(heatmaply)
library(htmlwidgets)
library(hrbrthemes)
```

#Import Datasets
```{r datasets, echo=FALSE,message=FALSE,warning=FALSE,include=FALSE}
HCS <- read.csv("Camilo/Analisis/Filtered_CORE_ASV_Abundance.csv", 
                header = TRUE, 
                sep = ";", 
                dec = ".", 
                skip = 0,
                row.names = 1)
TAXA <- read.csv("Camilo/Analisis/Filtered_CORE_TAXA.csv", 
                 header = TRUE, 
                 sep = ";", 
                 skip = 0, 
                 row.names = 1)

print(all(colnames(HCS)%in%rownames(TAXA)))
```

#Taxonomy function
```{r tax.sum, echo=FALSE,message=FALSE,warning=FALSE,include=FALSE}
Tax.sum <- function(OTU.Table, Tax.Table, Tax.lvl ){
  z <- NULL
  y <- NULL
  for (i in 1:length(unique(Tax.Table[colnames(OTU.Table),Tax.lvl]))) {
    if (length(OTU.Table[,which(Tax.Table[colnames(OTU.Table),Tax.lvl]==unique(Tax.Table[colnames(OTU.Table),Tax.lvl])[i])])!=length(rownames(OTU.Table))) {
      z <- which(Tax.Table[colnames(OTU.Table),Tax.lvl]==unique(Tax.Table[colnames(OTU.Table),Tax.lvl])[i])
      y <- cbind(y, apply(OTU.Table[,which(Tax.Table[colnames(OTU.Table),Tax.lvl]==unique(Tax.Table[colnames(OTU.Table),Tax.lvl])[i])], 1, function(x) sum(x)))
    } else {
      y <- cbind(y, OTU.Table[,which(Tax.Table[colnames(OTU.Table),Tax.lvl]==unique(Tax.Table[colnames(OTU.Table),Tax.lvl])[i])])
    }
  }
  colnames(y) <- unique(Tax.Table[colnames(OTU.Table),Tax.lvl])
  invisible((y))
}
```

#Relative abundance function
```{r rltv fx, echo=FALSE,message=FALSE,warning=FALSE,include=FALSE}
rltv.Otu.Table <- function(x) {
  x.Data.rltv <- NULL
  for (i in 1:dim(x)[1]) {
    x.Data.rltv <- rbind(x.Data.rltv, x[i,]/apply(x, 1, function(x) sum(x))[i])
  }
  rownames(x.Data.rltv) <- rownames(x)
  invisible(x.Data.rltv)
}
```

#Selecting PPE ASV
##TAXA
```{r ppe taxa, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
ppe.taxa <- dplyr::filter(TAXA, Division == "Chlorophyta" | Division == "Ochrophyta" | Division == "Cryptophyta" | Division == "Cryptophyta:nucl" | Division == "Haptophyta" | Division == "Katblepharidophyta") #Used to be 1643, but without Rhodophyta now are 1428
ppe.taxa <- dplyr::filter(ppe.taxa, Class != "Ulvophyceae") #Now we have 1345 different ASV
write.csv2(ppe.taxa, "HCS_PPE_TAXA.csv")
```

##ASV Abundance
```{r ppe asv, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
ppe.asv <- dplyr::select(HCS, all_of(ppe.taxa$Seq))
write.csv2(ppe.asv, "HCS_PPE_ASV_Abundance.csv")
```

#Data joint
```{r ppe joint, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
ppe.un <- as.data.frame(t(ppe.asv)) %>% dplyr::mutate(Seq = all_of(ppe.taxa$Seq), .before = "C1A17")
ppe.un <- dplyr::mutate(ppe.un, 
                        Chanaral = rowSums(ppe.un[c(2:13)]), 
                        Flamenco = rowSums(ppe.un[c(14:25)]), 
                        Huasco = rowSums(ppe.un[c(26:37)]), 
                        Pta.Choros = rowSums(ppe.un[c(38:42)]), 
                        Quintero = rowSums(ppe.un[c(43:52)]), 
                        LasCruces = rowSums(ppe.un[c(53:64)]), 
                        Total = rowSums(ppe.un[c(2:64)])
                        )
ppe.un <- dplyr::inner_join(ppe.un, ppe.taxa, by = "Seq") %>% dplyr::relocate(ASV, .after = Seq)
rownames(ppe.un) <- dplyr::all_of(ppe.un[,1])
write.csv2(ppe.un, "HCS_PPE_Taxonomic_And_Abundance.csv")
```

#UpSet plot
##UpSet preparation
```{r upset prep, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
verdes <- ppe.un[,2]
vedited <- ppe.un[,-c(2,72:80)]
rownames(vedited) <- verdes
write.csv2(vedited, "HCS_PPE_edited_taxonomic_and_abundance.csv")
#Dataframe de presencia-ausencia de ASV de PPE
ppe.apats <- vedited[,-1]
ppe.apats <- vegan::decostand(ppe.apats, method = "pa") %>% 
  add_column(Seq = dplyr::all_of(vedited$Seq), 
             .before = "C1A17")
write.csv2(ppe.apats, "HCS_PPE_Absence_Presence.csv")
```

##PPE UpSet (According to previously plotted)
```{r ppe upset, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
#Its easier for UpSetR re-reading the dataframe...
aps.ppe <- read.csv("HCS_PPE_Absence_Presence.csv", header = TRUE, sep = ";", dec = ".", skip = 0)

png("~/Documents/GitHub/CORE/Camilo/Analisis/Figuras/Figura_21_PPE_UpSet.png", width = 30, height = 17, units = "in", res = 600)
upset(aps.ppe, 
      nsets = 6, 
      nintersects = NA, 
      sets = c("LasCruces", "Quintero", "Pta.Choros", "Huasco", "Flamenco", "Chanaral"), 
      intersections = list("LasCruces", "Quintero", "Pta.Choros", "Huasco", "Flamenco", "Chanaral", 
                           list("Chanaral", "Flamenco"), 
                           list("Huasco", "Pta.Choros"), 
                           list("Quintero", "LasCruces"), 
                           list("Chanaral", "Huasco"), 
                           list("Chanaral", "Quintero"), 
                           list("Huasco", "Quintero"), 
                           list("Flamenco", "Pta.Choros"), 
                           list("Flamenco", "LasCruces"), 
                           list("Pta.Choros", "LasCruces"), 
                           list("Quintero", "LasCruces"), 
                           list("Chanaral", "Huasco", "Quintero"), 
                           list("Flamenco", "Pta.Choros", "LasCruces"), 
                           list("Chanaral", "Flamenco", "Huasco", "Pta.Choros"), 
                           list("Chanaral", "Flamenco", "Huasco", "Pta.Choros", "Quintero"), 
                           list("Chanaral", "Flamenco", "Huasco", "Pta.Choros", "LasCruces"), 
                           list("Chanaral", "Flamenco", "Huasco", "Pta.Choros", "Quintero", "LasCruces")
                           ), 
      empty.intersections = "on", 
      keep.order = TRUE, 
      query.legend = "top", 
      queries = list(list(query = intersects, 
                          params = "Chanaral", 
                          color = "#FF8811", 
                          active = TRUE, 
                          query.name = "Unique Cha침aral ASV"), 
                     list(query = intersects, 
                          params = "Flamenco", 
                          color = "#F4D06F", 
                          active = TRUE, 
                          query.name = "Unique Flamenco ASV"), 
                     list(query = intersects, 
                          params = "Huasco", 
                          color = "#392F5A", 
                          active = TRUE, 
                          query.name = "Unique Huasco ASV"), 
                     list(query = intersects, 
                          params = "Pta.Choros", 
                          color = "#403286", 
                          active = TRUE, 
                          query.name = "Unique Punta Choros ASV"), 
                     list(query = intersects, 
                          params = "Quintero", 
                          color = "#18E0BD", 
                          active = T, 
                          query.name = "Unique Quintero ASV"), 
                     list(query = intersects, 
                          params = "LasCruces", 
                          color = "#80EB9F", 
                          active = TRUE, 
                          query.name = "Unique Las Cruces ASV"), 
                     list(query = intersects, 
                          params = list("Chanaral", 
                                        "Flamenco", 
                                        "Huasco", 
                                        "Pta.Choros", 
                                        "Quintero", 
                                        "LasCruces"), 
                          color="#EF233C", 
                          active = TRUE, 
                          query.name = "Shared PPE ASV")
                     ), 
      point.size = 3.5, 
      line.size = 1.5, 
      text.scale = 3, 
      mainbar.y.label = "Sites intersections", 
      sets.x.label = "PPE ASV per sampling site")
dev.off()
```

#PPE ASV type identification (shared, unique and other)
##ASV per site
###Cha침aral
```{r cha ppe, echo=FALSE,message=FALSE,warning=FALSE,include=FALSE}
chappe <- aps.ppe %>% dplyr::filter(Chanaral == 1)
chappe.asv <- dplyr::select(ppe.asv, all_of(chappe$Seq))
write.csv2(chappe.asv, "HCS_Chanaral_PPE_ASV_Abundance.csv")
```

###Flamenco
```{r fla pee, echo=FALSE,message=FALSE,warning=FALSE,include=FALSE}
flappe <- aps.ppe %>% dplyr::filter(Flamenco == 1)
flappe.asv <- dplyr::select(ppe.asv, all_of(flappe$Seq))
write.csv2(flappe.asv, "HCS_Flamenco_PPE_ASV_Abundance.csv")
```
###Huasco
```{r hu ppe, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
huppe <- aps.ppe %>% dplyr::filter(Huasco == 1)
huppe.asv <- dplyr::select(ppe.asv, all_of(huppe$Seq))
write.csv2(huppe.asv, "HCS_Huasco_PPE_ASV_Abundance.csv")
```

###Punta de Choros
```{r pch ppe, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
pchppe <- aps.ppe %>% dplyr::filter(Pta.Choros == 1)
pchppe.asv <- dplyr::select(ppe.asv, all_of(pchppe$Seq))
write.csv2(pchppe.asv, "HCS_Pta_Choros_PPE_ASV_Abundance.csv")
```

###Quintero
```{r qin ppe, echo=FALSE,message=FALSE,warning=FALSE,include=FALSE}
qinppe <- aps.ppe %>% dplyr::filter(Quintero == 1)
qinppe.asv <- dplyr::select(ppe.asv, all_of(qinppe$Seq))
write.csv2(qinppe.asv, "HCS_Quintero_PPE_ASV_Abundance.csv")
```

###Las Cruces
```{r lc ppe, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
lcppe <- aps.ppe %>% dplyr::filter(LasCruces == 1)
lcppe.asv <- dplyr::select(ppe.asv, all_of(lcppe$Seq))
write.csv2(lcppe.asv, "HCS_Las_Cruces_PPE_ASV_Abundance.csv")
```

##Shared
```{r shared ppe, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
shappe <- aps.ppe %>% dplyr::filter(Chanaral == 1 & Flamenco == 1 & Huasco == 1 & Pta.Choros == 1 & Quintero == 1 & LasCruces == 1)
shappe.asv <- dplyr::select(ppe.asv, all_of(shappe$Seq))
write.csv2(shappe.asv, "Shared_HCS_PPE_ASV_Abundance.csv")
```

##Unique
###Cha침aral
```{r uni cha ppe, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
u.chappe <- aps.ppe %>% dplyr::filter(Chanaral == 1 & Flamenco == 0 & Huasco == 0 & Pta.Choros == 0 & Quintero == 0 & LasCruces == 0)
u.chappe.asv <- dplyr::select(chappe.asv, all_of(u.chappe$Seq))
write.csv2(u.chappe.asv, "HCS_Unique_Chanaral_PPE_ASV_Abundance.csv")
```

###Flamenco
```{r uni fla ppe, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
u.flappe <- aps.ppe %>% dplyr::filter(Chanaral == 0 & Flamenco == 1 & Huasco == 0 & Pta.Choros == 0 & Quintero == 0 & LasCruces == 0)
u.flappe.asv <- dplyr::select(flappe.asv, all_of(u.flappe$Seq))
write.csv2(u.flappe.asv, "HCS_Unique_Flamenco_PPE_ASV_Abundance.csv")
```

###Huasco
```{r uni hu ppe, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
u.huppe <- aps.ppe %>% dplyr::filter(Chanaral == 0 & Flamenco == 0 & Huasco == 1 & Pta.Choros == 0 & Quintero == 0 & LasCruces == 0)
u.huppe.asv <- dplyr::select(huppe.asv, all_of(u.huppe$Seq))
write.csv2(u.huppe.asv, "HCS_Unique_Huasco_PPE_ASV_Abundance.csv")
```

###Punta de Choros
```{r uni pch ppe, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
u.pchppe <- aps.ppe %>% dplyr::filter(Chanaral == 0 & Flamenco == 0 & Huasco == 0 & Pta.Choros == 1 & Quintero == 0 & LasCruces == 0)
u.pchppe.asv <- dplyr::select(pchppe.asv, all_of(u.pchppe$Seq))
write.csv2(u.pchppe.asv, "HCS_Unique_Pta_Choros_PPE_ASV_Abundance.csv")
```

###Quintero
```{r uni qin ppe, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
u.qinppe <- aps.ppe %>% dplyr::filter(Chanaral == 0 & Flamenco == 0 & Huasco == 0 & Pta.Choros == 0 & Quintero == 1 & LasCruces == 0)
u.qinppe.asv <- dplyr::select(qinppe.asv, all_of(u.qinppe$Seq))
write.csv2(u.qinppe.asv, "HCS_Unique_Quintero_PPE_ASV_Abundance.csv")
```

###Las Cruces
```{r uni lc ppe, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
u.lcppe <- aps.ppe %>% dplyr::filter(Chanaral == 0 & Flamenco == 0 & Huasco == 0 & Pta.Choros == 0 & Quintero == 0 & LasCruces == 1)
u.lcppe.asv <- dplyr::select(lcppe.asv, all_of(u.lcppe$Seq))
write.csv2(u.lcppe.asv, "HCS_Las_Cruces_PPE_ASV_Abundance.csv")
```

##Other intersections
```{r other ppe, echo=FALSE,message=FALSE,warning=FALSE,include=FALSE}

```

